female code

### 2024-01-15 code/codeprocessfemale.Rmd
editing female code to have more visually appealing plots

```{r packages}
# Load packages
library(tidyverse)
library(dplyr)
library(ggplot2)
library(readr)
library(cowplot)
```
```{r Functions}
# Read the CSV file
data <- read.csv("../gym2024data/cleandata/data_2022_2023.csv", header = TRUE)

@@

#Create a table with the top 10 athletes with the highest mean scores for each apparatus and to plot each apparatus on separate graphs
  # Filter for USA female gymnasts
  usa_female_scores <- data %>%
  filter(Country == "USA" & Gender == "w")

@@

  # Plot each apparatus on one graph
  for (apparatus in unique(top_10_athletes$Apparatus)) {
  data_subset <- filter(top_10_athletes, Apparatus == apparatus)
  p <- ggplot(top_10_athletes, aes(x = SD_Score, y = Mean_Score, label = LastName)) +
  geom_point() +
  geom_text(hjust = 0, vjust = 0) +
  labs(title = "Top 10 Female Athletes",
       x = "Standard Deviation", y = "Mean Score") +
  facet_wrap(~Apparatus, scales = "free") +
  theme_minimal()
  }

@@

#Create a scatter plot of the summed means on the y-axis and summed standard deviations on the x-axis
  # Create a scatter plot
  p1 <- ggplot(sums, aes(x = Sum_SD, y = Sum_Means, label = LastName)) +
  geom_point() +
  geom_text(hjust = 0, vjust = 0) +
  labs(x = "Sum of Standard Deviations", y = "Sum of Means", title = "Female All-Around Candidates")

@@

  # Create a scatter plot for the top 10 combinations
  p2 <- ggplot(top_10_combinations, aes(x = SD_Sum, y = Mean_Score)) +
  geom_point() +
  geom_text(aes(label = Combination), hjust = 0, vjust = 0) +
  labs(x = "Sum of Standard Deviations", y = "Mean Score") +
  ggtitle("Combinations of 3 Female Athletes")

@@

  # Create a scatter plot for the top 10 combinations
  p3 <- ggplot(top_10_combinations_4, aes(x = SD_Sum, y = Mean_Score)) +
  geom_point() +
  geom_text(aes(label = Combination), hjust = 0, vjust = 0) +
  labs(x = "Sum of Standard Deviations", y = "Mean Score") +
  ggtitle("Combinations of 4 Female Athletes")

>>>>

```{r packages}
# Load packages
library(tidyverse)
library(dplyr)
library(ggplot2)
library(readr)
library(cowplot)
library(ggrepel)
```
```{r Functions}
# Read the CSV file
data <- read.csv("../gym2024data/cleandata/data_2022_2023.csv", header = TRUE)

@@

#Create a table with the top 10 athletes with the highest mean scores for each apparatus to plot each apparatus on separate graphs
  # Filter for USA female gymnasts
  usa_female_scores <- data %>%
  filter(Country == "USA" & Gender == "w")

@@

  # Plot each apparatus on one graph
  p <- ggplot(top_10_athletes, aes(x = SD_Score, y = Mean_Score, label = LastName)) +
  geom_point() +
  geom_text_repel(box.padding = 0.25, point.padding = 0.25) +  
  labs(title = "Top 10 Female Athletes",
       x = "Standard Deviation", y = "Mean Score") +
  facet_wrap(~Apparatus, scales = "free") +
  theme_minimal() +
  theme(
    panel.background = element_rect(fill = "gray85"),  
    panel.grid.major = element_line(color = "white"),
    axis.text = element_text(color = "black"),  
    axis.title = element_text(color = "black"), 
    plot.title = element_text(color = "black")  
  )

@@

#Create a scatter plot of the summed means on the y-axis and summed standard deviations on the x-axis
  # Create a scatter plot
  p1 <- ggplot(sums, aes(x = Sum_SD, y = Sum_Means, label = LastName)) +
  geom_point() +
  geom_text_repel(box.padding = 0.25, point.padding = 0.25) +
  labs(x = "Sum of Standard Deviations", y = "Sum of Means", title = "Female All-Around Candidates") +
  facet_wrap(~., scales = "free") +  
  theme_minimal() +
  theme(
    panel.background = element_rect(fill = "gray85"),  
    panel.grid.major = element_line(color = "white"),
    axis.text = element_text(color = "black"),  
    axis.title = element_text(color = "black"), 
    plot.title = element_text(color = "black")  
  )

@@

  # Create a scatter plot for the top 10 combinations
  p2 <- ggplot(top_10_combinations, aes(x = SD_Sum, y = Mean_Score)) +
    geom_point() +
    geom_text_repel(aes(label = Combination), box.padding = 0.25, point.padding = 0.25) +
    labs(x = "Sum of Standard Deviations", y = "Mean Score") +
    ggtitle("Combinations of 3 Female Athletes") +
    facet_wrap(~., scales = "free") +  
    theme_minimal() +
    theme(
        panel.background = element_rect(fill = "gray85"),  
        panel.grid.major = element_line(color = "white"),
        axis.text = element_text(color = "black"),  
        axis.title = element_text(color = "black"), 
        plot.title = element_text(color = "black")  
    )

@@

  # Create a scatter plot for the top 10 combinations
  p3 <- ggplot(top_10_combinations_4, aes(x = SD_Sum, y = Mean_Score)) +
    geom_point() +
    geom_text_repel(aes(label = Combination), box.padding = 0.25, point.padding = 0.25) +
    labs(x = "Sum of Standard Deviations", y = "Mean Score") +
    ggtitle("Combinations of 4 Female Athletes") +
    facet_wrap(~., scales = "free") +  
    theme_minimal() +
    theme(
        panel.background = element_rect(fill = "gray85"),  
        panel.grid.major = element_line(color = "white"),
        axis.text = element_text(color = "black"),  
        axis.title = element_text(color = "black"), 
        plot.title = element_text(color = "black")  
    )
